### 2023-01-11 paper-thesis/chapters/21-adding-inference.tex
More writing on inference

>>>>

Next when we type-check an \verb|Infer| expression we just type-check the meta-variable inside. This will wait until the value of the meta-variable is known before type-checking, which is the behavior we want.
\begin{lstlisting}
typeOfExpr_(s, Infer(q)) = (Infer(q), t) :-
	typeOfExpr_(s, q) == (_, t).
\end{lstlisting}

When beta reducing we deliberately keep the \verb|Infer| expression intact, since we want to keep the information that it is an expression that might have to be inferred during beta equality checks.
\begin{lstlisting}
betaReduce_((_, Infer(e))) = Infer(e).
\end{lstlisting}

Finally, the difficult part of handling inference in beta equality. There are four different cases that involve \verb|Infer| expressions in beta equality, these are:

\begin{enumerate}
	\item A value \verb|e1| on the left, an infer expression on the right. In this case we simply want to set the metavariable equal to \verb|e1|. For example:
	\begin{lstlisting}
expectBetaEq((s1, e1@Type(_)), (_, Infer(e2))) :- e1 == e2.
expectBetaEq((s1, e1@BoolTrue()), (_, Infer(e2))) :- e1 == e2.
expectBetaEq((s1, e1@BoolFalse()), (_, Infer(e2))) :- e1 == e2.
expectBetaEq((s1, e1@BoolType()), (_, Infer(e2))) :- e1 == e2.
	\end{lstlisting}
	\item A complex expression \verb|e1| on the left, an infer expression on the right. 
	\item An infer expression on the left, any expression on the right.
	\item An infer expression on the left and on the right.
\end{enumerate}
